Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-11-30 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
small rewordings in conclusions

While search for optimal solutions is beyond reach due to the size and complexity of
practical scheduling applications,
reliably computing high-quality approximations is an important subject of future work.
This includes automatic methods for deciding about the features to consider for
partitioning operations into clusters, i.e., determining whether an eligible feature is
informative or noisy, respectively.
As we can hardly expect that even moderately sized time windows can be solved to
optimality in a short amount of time or eventual optimization criteria values be
accurately predicted from solutions for sub-problems,
it can still be worthwhile to incorporate measures allowing for corrections of 
partitioning decisions, which can consist of overlapping time windows to enable
revisions or dynamically relaunching the clustering algorithm wrt.\ computed
partial schedules.
Instead of obtaining features by greedy search methods only, we may also take
the outcomes of one or several multi-shot optimization runs into account as
features for another clustering and solving round until a fixpoint without
further improvement is reached.
That is, there are various opportunities to extend our approach in the future,
where going beyond the classical Job-shop Scheduling Problem, e.g., by
considering flexible machine allocations or partially ordered operations,
can also be relevant for practical application scenarios.

>>>>

While search for optimal solutions is beyond reach due to the size and complexity of
practical scheduling applications,
reliably computing high-quality approximations is an important subject of future work.
This includes automatic methods for deciding about the features to consider for
partitioning operations into clusters, i.e., determining whether an eligible feature is
informative or noisy, respectively.
As we can hardly expect that even moderately sized time windows can be solved to
optimality in a short amount of time or eventual optimization criteria values be
accurately predicted from solutions for sub-problems,
it can still be worthwhile to incorporate measures allowing for corrections of 
partitioning decisions, which could consist of overlapping time windows to enable
revisions or dynamically relaunching the clustering algorithm wrt.\ computed
partial schedules.
Instead of obtaining features by greedy search methods only, we may also take
the outcomes of one or several multi-shot optimization runs into account as
features for another clustering and solving round until a fixpoint without
further improvement is reached.
That is, there are various opportunities to extend our approach in the future,
where going beyond the classical Job-shop Scheduling Problem, e.g., by
considering flexible resource allocations or partially ordered operations,
can also be of interest for practical application scenarios.
